Intelligent Building Energy Management System

### 2021-04-26 finalPresentation.tex
Updated finalPresentation.tex including circuit diagram

\title[Final Presentation]{Intelligent Building Energy Management System}

@@

\author[B.~Lauer, E.~Watkins]{Brian~Lauer \and Elliot~Watkins \and
Advisor: Dr. Suruz Miah}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSubsection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

@@

% \begin{frame}{Outline} %
%   \tableofcontents%[pausesections]
%   % You might wish to add the option [pausesections]
% \end{frame}

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Introduction}
\section{Architecture}
\section{Embedded/Robotics Computer}
\section{WeMo Insight Switch}
\section{Overall Setup}
\section{Home Page}
\section{Active Devices Page}
\section{WeMo Power Plot}
\section{Scheduling/Applications Page}
\section{Conclusion}

\begin{frame}{Introduction}{} % Elliot
    % Applications of Building Energy Management
    \begin{multicols}{2}
        \begin{small}
            \begin{itemize}
                \item Problems that iBEMS will address
                    \begin{itemize}
                        \item Can help save on energy costs
                        \item Less impact on environment
                    \end{itemize}
                \item How can the IoT help?
                    \begin{itemize}
                        \item WiFi integrated into most buildings
                        \item Our Web-based approach simplifies development and end-user experience
                    \end{itemize}
                \item Overall Goal
                    \begin{itemize}
                        \item Create a platform in which users can login and access 2 or 3 IoT devices connected to a building’s energy supply
                        \item Allow the user to closely monitor energy usage for a residential building.
                    \end{itemize}
            \end{itemize}
        \end{small}
        \begin{figure}
        \centering
        \includegraphics[scale=0.4]{figs/BEMS_Image.jpg}
        \caption{General BEMS}
        \label{fig:high_level_arch}
    \end{figure}
    \end{multicols}
\end{frame}

\begin{frame}{Architecture}{} % Brian
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.3]{figs/highLevelArchitecture.pdf}
            \caption{High Level Architecture}
            \label{fig:high_level_arch}
        \end{figure}
        \textsc{}
        \begin{itemize}
            \item iBEMS currently has support for 2 IoT devices (WeMo Insight Switch and embedded computer) and can download weather data for the user
            \item A microgrid with a smart meter will be simulated in the near future
        \end{itemize}        
    \end{multicols}
\end{frame}

@@

\begin{frame}{Embedded Computer Receiver Program}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.45]{figs/Beaglebone_Receiver_Diagram.png}
        \caption{Receiver Running on Embedded Computer}
        \label{fig:Beaglebone_Receiver_Diagram}
    \end{figure}
\end{frame}

\begin{frame}{Embedded Computer Circuit for Power Usage Data}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.7]{figs/Beaglebone_Circuit.png}
        \caption{Circuit to Measure Power Usage}
        \label{fig:Beaglebone_Circuit}
    \end{figure}
    \begin{itemize}
        \item The embedded computer does not have the ability to measure power, but it does have ADC
        \item Here, the power from the motor driver is being run through a resistor. The ADC reads the voltage across the resistor and since resistance is known, current can be calculated for 1 motor
    \end{itemize}
\end{frame}

@@

% \begin{frame}{Frame Title}
%     \begin{figure}
%         \centering
%         \includegraphics{}
%         \caption{Caption}
%         \label{fig:my_label}
%     \end{figure}
% \end{frame}

@@

\begin{frame}{Overall Setup}{} % Elliot 
    \begin{figure}
        \centering
        \includegraphics[scale=0.04]{figs/overallView.jpg}
        \caption{Overall View}
        \label{fig:my_label}
    \end{figure}
    Tested the WeMo Insight Switch with a bank of lights and the embedded computer with a robot chassis

\end{frame}

@@

\begin{frame}{Conclusion}{} % Elliot
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.8]{figs/logo.pdf}
            \label{fig:logo}
        \end{figure}
        \begin{small}
            \begin{itemize}
                \item Advantages: open source, simple interface, modular agent-based code base
                \item Disadvantages: can only operate on a LAN, lacks features of a commercial BEMS system
                \item Challenges: adapting the platform for an enterprise network in a commercial building, security features 
            \end{itemize}
        \end{small}
    \end{multicols}
\end{frame}

\begin{frame}{Conclusion}{}
    Future Improvements:
    \begin{itemize}
        \item Refactor the user interface
        \item Granular user access control
        \item Refactor agent communication
        \item Intelligent algorithms
        \item Mobile app
        \item Persistent device information storage
    \end{itemize}
\end{frame}

>>>>

\usepackage{siunitx}
\sisetup{unitsep=\cdot}

\usepackage{tikz}
% load libraries
\usetikzlibrary{backgrounds,calc,patterns,decorations.pathmorphing,decorations.markings,shapes,arrows,snakes,tikzmark}
\usepackage[siunitx,smartlabels]{circuitikzgit}
\def\smgrid{0.5}
% For compact drawing of resistors and capacitors 1
\ctikzset{resistors/scale=0.5,
  capacitors/scale=0.6,
  sources/scale=0.9} 
\ctikzset{
  amplifiers/fill=cyan,
  sources/fill=green!50,
  diodes/fill=red,
  resistors/fill=violet,
}

\title[iBEMS]{Intelligent Building Energy Management System}

@@

\author[B.~Lauer, E.~Watkins]{Brian~Lauer \and Elliot~Watkins\\
Advisor: Dr. Suruz Miah}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

@@

\begin{frame}{Outline} %
  \tableofcontents%[pausesections]
  % You might wish to add the option [pausesections]
\end{frame}

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Introduction}

\begin{frame}{Introduction}{} % Elliot
    % Applications of Building Energy Management
    % \begin{multicols}{2}
      % \begin{block}{}
  \begin{columns}
    \column{0.5\textwidth}
    \begin{block}{}
      \begin{small}
        \begin{itemize}
        \item Problems that iBEMS will address
          \begin{itemize}
          \item Can help save on energy costs
          \item Less impact on environment
          \end{itemize}
        \item How can the IoT help?
          \begin{itemize}
          \item WiFi integrated into most buildings
          \item Our Web-based approach simplifies development and end-user experience
          \end{itemize}
        \end{itemize}
      \end{small}
    \end{block}
    \column{0.5\textwidth}
    {\small
      \begin{block}{Overall Goal}
        Overall Goal:
        \begin{itemize}
        \item Create a platform in which users can login and access $2$ or $3$ IoT devices connected to a building's energy supply
        \item Allow user to closely monitor energy usage for residential building
        \end{itemize}
      \end{block}
      }
    \begin{figure}
      \centering
      \includegraphics[scale=0.25]{figs/BEMS_Image.jpg}
      \caption{General BEMS}
      \label{fig:high_level_arch}
    \end{figure}
  \end{columns}

      % \end{block}
    % \end{multicols}
\end{frame}

\section{Architecture}
\begin{frame}{Architecture}{} % Brian
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.3]{figs/highLevelArchitecture.pdf}
            \caption{High Level Architecture}
            \label{fig:high_level_arch}
        \end{figure}
        \textsc{}
        \begin{itemize}
            \item iBEMS currently has support for 2 IoT devices (WeMo Insight Switch and embedded computer) and can download weather data for the user
            \item A microgrid with a smart meter will be simulated in the near future
        \end{itemize}        
    \end{multicols}
\end{frame}

@@

\section{Embedded/Robotics Computer}
\begin{frame}{Embedded Computer Receiver Program}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.45]{figs/Beaglebone_Receiver_Diagram.png}
        \caption{Receiver Running on Embedded Computer}
        \label{fig:Beaglebone_Receiver_Diagram}
    \end{figure}
\end{frame}

\begin{frame}{Embedded Computer Circuit for Power Usage Data}{}
    \begin{circuitikz}[american]
      \tikzstyle{every node} = [font = \tiny]
      % \usetikzlibrary{patterns}

      \draw
      (0,0) to[sqV,invert,l=PWM Signal from embedded computer] ++(0,4*\smgrid)
      to[Telmech=M,n=motor,fill=red!20] ++(4*\smgrid,0)
      to[C,l=$1~{[}\micro\farad{]}$,*-*] ++(0,-4*\smgrid) to[short]++(-4*\smgrid,0); 
      \draw
      (4*\smgrid,4*\smgrid) to[short,-*]++(3*\smgrid,0)
      to[short,-o]++(2*\smgrid,0)node[right]{Embedded Computer ADC (Ch\#0)};
      \draw
      (7*\smgrid,4*\smgrid) to[R,l=$2~{[}\ohm{]}$,-*]++(0,-4*\smgrid)
      to[short]++(-4*\smgrid,0);
      \draw
      (7*\smgrid,0) to[short,-o]++(2*\smgrid,0) node[right]{Embedded
        Computer ADC (Ground)};
    \end{circuitikz}

    % \begin{figure}
    %     \centering
    %     \includegraphics[scale=0.7]{figs/Beaglebone_Circuit.png}
    %     \caption{Circuit to Measure Power Usage}
    %     \label{fig:Beaglebone_Circuit}
    % \end{figure}
    \begin{itemize}
        \item The embedded computer does not have the ability to measure power, but it does have ADC
        \item Here, the power from the motor driver is being run through a resistor. The ADC reads the voltage across the resistor and since resistance is known, current can be calculated for 1 motor
    \end{itemize}
\end{frame}

@@

% \begin{frame}{Frame Title}
%     \begin{figure}
%         \centering
%         \includegraphics{}
%         \caption{Caption}
%         \label{fig:my_label}
%     \end{figure}
% \end{frame}
\section{WeMo Insight Switch}

@@

\section{Overall Experimental Setup}
\begin{frame}{Overall Experimental Setup}{} % Elliot 
    \begin{figure}
        \centering
        \includegraphics[scale=0.04]{figs/overallView.jpg}
        \caption{Overall View}
        \label{fig:my_label}
    \end{figure}
    Tested the WeMo Insight Switch with a bank of lights and the embedded computer with a robot chassis

\end{frame}
\section{Home Page}

@@

\section{Conclusion}
\begin{frame}{Conclusion}{} % Elliot
  \begin{columns}
    \column{0.5\textwidth}
    \begin{figure}
      \centering
      \includegraphics[scale=0.8]{figs/logo.pdf}
      \label{fig:logo}
    \end{figure}
    \column{0.5\textwidth}
    \begin{itemize}
      \item Advantages: open source, simple interface, modular agent-based code base
      \item Disadvantages: can only operate on a LAN, lacks features of a commercial BEMS system
      \item Challenges: adapting the platform for an enterprise network in a commercial building, security features 
    \end{itemize}
  \end{columns}  
\end{frame}

\begin{frame}
  \begin{block}{Further Improvements}
    \begin{itemize}
    \item Refactor the user interface
    \item Granular user access control
    \item Refactor agent communication
    \item Intelligent algorithms
    \item Mobile app
    \item Persistent device information storage
    \end{itemize}
  \end{block}
\end{frame}
